---
title: "Comparison of TIM Metrics"
author: "Chris Terry"
date: "6 February 2017"
output:
  html_document:
     number_sections: yes
     theme: cerulean
     toc: yes
---

# Introduction

This script runs the models detailed in [[]], calculates a number of TIM metrics and plots them.

It  has not been particularly tidied, nor is it particularly efficient, but should be readable.

Any questions to Chris Terry (james.terry@zoo.ox.ac.uk)

```{r, message=FALSE, warning=FALSE, echo=FALSE}
rm(list = ls())
library(deSolve)
library(magrittr)
library(rootSolve)
library(pracma)
library(Matrix)
library(dplyr)
library(tidyr)
library(Deriv)
library(abind)
library(ggplot2)
library(cowplot)
library(RColorBrewer)

```

# Linear Model
Tri-trophic Lotka-volterra with logistic resource growth and linear TIM of resource modifying predator-herbivore link:

```{r}
BasicLinTIM<-function(Time=c(), Abund, Pars){  
  with(as.list(c(Abund, Pars)),{  
    dA<- B*A*(a+(c*C)) -  m*A  
    dB<- B*C*b - B*A*(a+c*C) - n*B
    dC<- r*C*(1-(C/K)) -  B*C*b
    return(list(c(dA, dB, dC)))
  })  
}  

BasicLinTIM_2<-function(Abund, Parms){  
  with(as.list(c(Abund, Parms)),{
    dA<- B*A*(a+(c*C)) -  m*A  
    dB<- B*C*b - B*A*(a+c*C) - n*B
    dC<- r*C*(1-(C/K)) -  B*C*b
    return(c(dA, dB, dC))
  })  
}

dAdt<-expression(  B*A*(a+(c*C)) -  m*A      )
dBdt<-expression(  B*C*b - B*A*(a+c*C) - n*B    )
dCdt<-expression(  r*C*(1-(C/K)) -  B*C*b    )

{
  # Elements of Jacobian Needed
  cat(paste0('dAdt/dB = '))
  dAdt_dB<-Deriv(dAdt, x = 'B', cache.exp = FALSE)
  print(dAdt_dB)
  
  cat(paste0('dBdt/dA = '))
  dBdt_dA<-Deriv(dBdt, x = 'A', cache.exp = FALSE)
  print(dBdt_dA)
  
  cat(paste0('dAdt/dC = '))
  dAdt_dC<-Deriv(dAdt, x = 'C', cache.exp = FALSE)
  print(dAdt_dC)
  
  cat(paste0('dBdt/dC = '))
  dBdt_dC<-Deriv(dBdt, x = 'C', cache.exp = FALSE)
  print(dBdt_dC)
  
  # Derivatives of Jacobian w.r.t. Modifier
  
  cat(paste0('dAdt/dB/dC',' = '))
  dAdt_dB_dC<-Deriv(dAdt_dB, x = 'C', cache.exp = FALSE)
  print(dAdt_dB_dC)
  
  cat(paste0('dBdt/dA/dC ='))
  dBdt_dA_dC<-Deriv(dBdt_dA , x = 'C', cache.exp = FALSE)
  print(dBdt_dA_dC)
}
```

```{r}
pars<- list(a = 5, b = 3, r = 4, c = 0, m = 1, n = 1,  K = 1)
param.list = seq(-5, 5, l=80)

FUNC = BasicLinTIM_2
FUNC2 = BasicLinTIM
param = 'c'

CijkForm = 'Lin'
TITLE='\n TIM Strength Metrics for Linear System'
max=1
repeats=100


# Function to plot TIMs, mu, and populations of trophic cascade system against chaning parameter.   
# Takes C..dA.dB & C..dB.dA and pars from global environment. 

ModFunc <- function(c,C){1+c*C}

clist<- data.frame(param=param.list) # set of TIM parameters to run through
clist$A<-NA
clist$B<-NA
clist$C<-NA
clist$mu<-NA
clist$dAdt_dB_dCJAC<-NA
clist$dBdt_dA_dCJAC<-NA
clist$dBdt_dC<-NA
clist$dAdt_dC<-NA
clist$NewISRatio<-NA
clist$FluxAbsChange<-NA
clist$FluxRelChange<-NA
clist$dAdt_dB_dCInvJAC<- NA 
clist$dBdt_dA_dCInvJAC <- NA


# For finding New IS difference with TIM, calculate B equilbirum without TIM effect:
pars2=pars
pars2[['c']] <-0  # Cemove the TIM effect
outs2<- matrix(NA, ncol=3, nrow=repeats)
for(i in 1:repeats){
  outs2[i,]<-multiroot(FUNC, c(A=runif(1,0.01,max), B=runif(1,0.01,max),C=runif(1,0.01,max)),parms=pars2, positive = T)$root
}
un<-unique(outs2); colnames(un)<- c('A','B','C');
as.data.frame(un) %>% filter(A>0.0001) ->x # select positive equilbira
if(nrow(x)>0){
  HstarNoTIM =x$B[1]        # Just pick out one (NB if multiple equilibira may get problems here!)
  FluxNoMod <- x$B[1]*x$A[1]*pars2$a
}else{warning("Didn't find equilbirum")}



for(j in 1:nrow(clist)){
  pars[[param]] <- clist$param[j]  
  # Find Positive Equilbirum: 
  outs<- matrix(NA, ncol=3, nrow=repeats)
  for(i in 1:repeats){
    outs[i,]<-multiroot(FUNC, c(A=runif(1,0.01,max), B=runif(1,0.01,max),C=runif(1,0.01,max)),parms=pars, positive = T)$root
  }
  un<-unique(outs); colnames(un)<- c('A','B','C');
  as.data.frame(un) %>% filter(A>0.0001) ->x # select positive equilbira
  parsALL<- pars 
  if(nrow(x)>0){
    x %>% slice(1) ->x # Just pick out one (NB if multiple equilibira may get problems here!)
    clist$A[j]<-parsALL$A<-x[[1]]
    clist$B[j]<-parsALL$B<-x[[2]]
    clist$C[j]<-parsALL$C<-x[[3]]
    clist$mu[j] <- with(parsALL, ModFunc(c,C))
    clist$NewISRatio[j]<- x[[2]] / HstarNoTIM
    clist$NewISAbsDif ##!
    clist$dAdt_dB_dCJAC[j]<-with(parsALL,  eval(dAdt_dB_dC)) # dAdt_dB_dC
    clist$dBdt_dA_dCJAC[j]<-with(parsALL,  eval(dBdt_dA_dC)) # dBdt_dA_dC
    
    clist$dBdt_dC[j]<-with(parsALL,  eval(dBdt_dC))
    clist$dAdt_dC[j]<-with(parsALL,  eval(dAdt_dC))
    
    clist$FluxAbsChange[j] <- with(parsALL,  B*A*(a+c*C))- FluxNoMod
    clist$FluxRelChange[j] <- with(parsALL,  B*A*(a+c*C))/FluxNoMod
    
    x %>%slice(1) %>% as.numeric ->Eq
    
    abind(  # Create full 3-d array of derivatives of inverse jacobians
      matrix(rootSolve::gradient(function(x){
        jac<-jacobian.full(c(A=x, B=Eq[2], C=Eq[3]),FUNC2, parms=pars, pert=1e-6) # Increased perturbation necessary to reduce numerical errors
        inv(-jac)}, Eq[1]),nrow=3),
      matrix(rootSolve::gradient(function(x){
        jac<-jacobian.full(c(A=Eq[1], B=x, C=Eq[3]),FUNC2, parms=pars, pert=1e-6)
        inv(-jac)}, Eq[2]),nrow=3),
      matrix(rootSolve::gradient(function(x){
        jac<-jacobian.full(c(A=Eq[1], B=Eq[2], C=x),FUNC2, parms=pars, pert=1e-6)
        inv(-jac)}, Eq[3]),nrow=3),
      along=3)->y
    
    clist$dAdt_dB_dCInvJAC[j]<-y[1,2,3] #dAdt_dB_dC # pluck out the ones that are wanted
    clist$dBdt_dA_dCInvJAC[j]<-y[2,1,3] #dBdt_dA_dC
    
  }
}

names(clist)[1]<-param # Insert name of TIM parameter for plots

par(mfrow=c(5,3), mar=c(3,4,2,1), xpd=NA, oma=c(1,3,3,1), mgp=c(2, 1, 0), cex.main=1.8)

clist<-signif(clist, 6)

cats<-data.frame(Metric=c("A",                  
                          "B",            
                          "C",            
                          "mu",            
                          "dAdt_dB_dCJAC",   
                          "dBdt_dA_dCJAC",
                          "dBdt_dC",  
                          "dAdt_dC",  
                          "NewISRatio", 
                          "FluxAbsChange", 
                          "FluxRelChange" ,
                          "dAdt_dB_dCInvJAC",
                          "dBdt_dA_dCInvJAC"),metricCategory=
                   c('Population',
                     'Population'    ,
                     'Population'    ,
                     'Flux Change',
                     'Derivatives of Jacobian',
                     'Derivatives of Jacobian',
                     'Jacobian Elements',
                     'Jacobian Elements',
                     'Flux Change' ,
                     'Flux Change',
                     'Flux Change',
                     'Derivatives of Inverse Jacobian',
                     'Derivatives of Inverse Jacobian'),
                 Direction=
                   c('Neither',
                     'Neither'    ,
                     'Neither'    ,
                     'Neither',
                     'B on A',
                     'A on B',
                     'B change',
                     'A Change',
                     'Neither' ,
                     'Neither',
                     'Neither',
                     'B on A',
                     'A on B'))
#  mutate(Scaled = Value /scalers ) %>%

# clist %>% tbl_df %>%print
# 
# clist %>% 
#   #   select(-c(A,B,C))%>%
#   gather('Metric','Value', 2:14) %>% 
#   left_join( cats, by='Metric' ) %>%
#   arrange(Metric) %>%print
# 


clist %>% 
  #   select(-c(A,B,C))%>%
  gather('Metric','Value', 2:14) %>% 
  left_join( cats, by='Metric' ) %>%
  arrange(Metric) -> LINEARDATA


LINEARDATA %>%      
  mutate(absValues =abs(Value))%>%
  ggplot(aes(y=absValues, x=c, col=Metric, shape= Direction)) +
  geom_point() +
  geom_line() +
  #   scale_color_brewer(palette = 'Paired') +
  facet_grid(metricCategory~., scales = 'free_y') ->plot1

```


## Non-linear functional response Model

Tri-trophic Rozenweing MacArthur with exponential TIM of resource modifying predator-herbivore link:


```{r, echo=FALSE}

TyIIExp<-function(Time=c(), Abund, Pars){  
  with(as.list(c(Abund, Pars)),{  
    dA<- B*A*a*exp(c*C)/ (1+B*h*a*exp(c*C)) -  m*A  
    dB<- B*C*b/(1+C*b*h) - B*A*a*exp(c*C)/(1+B*h*a*exp(c*C)) - n*B
    dC<- r*C*(1-(C/K)) -  B*C*b / (1+C*b*h)  
    return(list(c(dA, dB, dC)))
  })  
}  

TyIIExp_2<-function(Abund, Parms){  
  with(as.list(c(Abund, Parms)),{
    dA<- B*A*a*exp(c*C)/ (1+B*h*a*exp(c*C)) -  m*A  
    dB<- B*C*b/(1+C*b*h) - B*A*a*exp(c*C)/(1+B*h*a*exp(c*C)) - n*B
    dC<- r*C*(1-(C/K)) -  B*C*b / (1+C*b*h)  
    return(c(dA, dB, dC))
  })  
}
####


dAdt<-expression(  B*A*a*exp(c*C)/ (1+B*h*a*exp(c*C)) -  m*A       )
dBdt<-expression(  B*C*b/(1+C*b*h) - B*A*a*exp(c*C)/(1+B*h*a*exp(c*C)) - n*B   )
dCdt<-expression(  r*C*(1-(C/K)) -  B*C*b / (1+C*b*h)    )

{
  # Elements of Jacobian Needed
  cat(paste0('dAdt/dB = '))
  dAdt_dB<-Deriv(dAdt, x = 'B', cache.exp = FALSE)
  print(dAdt_dB)
  
  cat(paste0('dBdt/dA = '))
  dBdt_dA<-Deriv(dBdt, x = 'A', cache.exp = FALSE)
  print(dBdt_dA)
  
  cat(paste0('dAdt/dC = '))
  dAdt_dC<-Deriv(dAdt, x = 'C', cache.exp = FALSE)
  print(dAdt_dC)
  
  cat(paste0('dBdt/dC = '))
  dBdt_dC<-Deriv(dBdt, x = 'C', cache.exp = FALSE)
  print(dBdt_dC)
  
  # Derivatives of Jacobian w.r.t. Modifier
  
  cat(paste0('dAdt/dB/dC',' = '))
  dAdt_dB_dC<-Deriv(dAdt_dB, x = 'C', cache.exp = FALSE)
  print(dAdt_dB_dC)
  
  cat(paste0('dBdt/dA/dC ='))
  dBdt_dA_dC<-Deriv(dBdt_dA , x = 'C', cache.exp = FALSE)
  print(dBdt_dA_dC)
}
```


```{r}

#pars<- list(a = 6, b = 5, r = 2, c = 0, m = 1,n = 1,h= 0.1,K = 1)

pars<- list(a = 6, b = 5, r = 2, c = 0, m = 1,n = 1,h= 0.4,K = 1)

FUNC=TyIIExp_2
FUNC2=TyIIExp 
param='c'
param.list=seq(-1, 1.5, l=80)
CijkForm='Exp'
TITLE='\n TIM Strength Metrics for Non-linear System'
max=1
repeats=100

# Function to plot TIMs, mu, and populations of trophic cascade system against chaning parameter.   
# Takes C..dA.dB & C..dB.dA and pars from global environment. 

ModFunc <- function(c,C){exp(c*C)}

clist<- data.frame(param=param.list) # set of TIM parameters to run through
clist$A<-NA
clist$B<-NA
clist$C<-NA
clist$mu<-NA
clist$dAdt_dB_dCJAC<-NA
clist$dBdt_dA_dCJAC<-NA
clist$dBdt_dC<-NA
clist$dAdt_dC<-NA
clist$NewISRatio<-NA
clist$FluxAbsChange<-NA
clist$FluxRelChange<-NA
clist$dAdt_dB_dCInvJAC<- NA 
clist$dBdt_dA_dCInvJAC <- NA


# For finding New IS difference with TIM, calculate B equilbirum without TIM effect:
pars2=pars
pars2[['c']] <-0  # Remove the TIM effect
outs2<- matrix(NA, ncol=3, nrow=repeats)
for(i in 1:repeats){
  outs2[i,]<-multiroot(FUNC, c(A=runif(1,0.01,max), B=runif(1,0.01,max),C=runif(1,0.01,max)),parms=pars2, positive = T)$root
}
un<-unique(outs2); colnames(un)<- c('A','B','C');
as.data.frame(un) %>% filter(A>0.0001) ->x # select positive equilbira
if(nrow(x)>0){
  BstarNoTIM =x$B[1]        # Just pick out one (NB if multiple equilibira may get problems here!)
  if(CijkForm=='Exp') FluxNoMod<-  x$B[1]*x$A[1]*pars2$a/(1+x$B[1]*pars2$h*pars2$a)# Calculate flux without mods
  if(CijkForm=='Lin') FluxNoMod <- x$B[1]*x$A[1]*pars2$a
}else{warning("Didn't find equilbirum")}

for(j in 1:nrow(clist)){
  pars[[param]] <- clist$param[j]  
  # Find Aositive Equilbirum: 
  outs<- matrix(NA, ncol=3, nrow=repeats)
  for(i in 1:repeats){
    outs[i,]<-multiroot(FUNC, c(A=runif(1,0.01,max), B=runif(1,0.01,max),C=runif(1,0.01,max)),parms=pars, positive = T)$root
  }
  un<-unique(outs); colnames(un)<- c('A','B','C');
  as.data.frame(un) %>% filter(A>0.0001) ->x # select positive equilbira
  parsALL<- pars 
  if(nrow(x)>0){
    x %>% slice(1) ->x # Just pick out one (NB if multiple equilibira may get problems here!)
    clist$A[j]<-parsALL$A<-x[[1]]
    clist$B[j]<-parsALL$B<-x[[2]]
    clist$C[j]<-parsALL$C<-x[[3]]
    clist$mu[j] <- with(parsALL, ModFunc(c,C))
    clist$NewISRatio[j]<- x[[2]] / BstarNoTIM
    clist$NewISAbsDif ##!
    clist$dAdt_dB_dCJAC[j]<-with(parsALL,  eval(dAdt_dB_dC)) # dAdt_dB_dC
    clist$dBdt_dA_dCJAC[j]<-with(parsALL,  eval(dBdt_dA_dC)) # dBdt_dA_dC
    
    clist$dBdt_dC[j]<-with(parsALL,  eval(dBdt_dC))
    clist$dAdt_dC[j]<-with(parsALL,  eval(dAdt_dC))
    
    clist$FluxAbsChange[j] <-with(parsALL, B*A*a*exp(c*C)/(1+B*h*a*exp(c*C)))- FluxNoMod
    clist$FluxRelChange[j] <-with(parsALL, B*A*a*exp(c*C)/(1+B*h*a*exp(c*C)))/FluxNoMod
    
    
    x %>%slice(1) %>% as.numeric ->Eq
    
    abind(  # Create full 3-d array of derivatives of inverse jacobians
      matrix(rootSolve::gradient(function(x){
        jac<-jacobian.full(c(A=x, B=Eq[2], C=Eq[3]),FUNC2, parms=pars, pert=1e-6) # Increased perturbation necessary to reduce numerical errors
        inv(-jac)}, Eq[1]),nrow=3),
      matrix(rootSolve::gradient(function(x){
        jac<-jacobian.full(c(A=Eq[1], B=x, C=Eq[3]),FUNC2, parms=pars, pert=1e-6)
        inv(-jac)}, Eq[2]),nrow=3),
      matrix(rootSolve::gradient(function(x){
        jac<-jacobian.full(c(A=Eq[1], B=Eq[2], C=x),FUNC2, parms=pars, pert=1e-6)
        inv(-jac)}, Eq[3]),nrow=3),
      along=3)->y
    
    clist$dAdt_dB_dCInvJAC[j]<-y[1,2,3] #dAdt_dB_dC # Aluck out the ones that are wanted
    clist$dBdt_dA_dCInvJAC[j]<-y[2,1,3] #dBdt_dA_dC
    
  }
}

names(clist)[1]<-param # Insert name of TIM parameter for plots


clist %>% 
  #   select(-c(A,B,C))%>%
  gather('Metric','Value', 2:14) %>% 
  left_join( cats, by='Metric' ) %>%
  arrange(Metric) -> NONLINEARDATA


NONLINEARDATA%>%
  mutate(absValues =abs(Value))%>%
  ggplot(aes(y=Value, x=c, col=Metric, shape= Direction)) +
  geom_point() +
  geom_line() +
  #   scale_color_brewer(palette = 'Paired') +
  facet_grid(metricCategory~., scales = 'free_y') -> plot1
```



#  Van Veen 

Uses model and fitted values from van Veen et al. 

van Veen, F. J. F., van Holland, P. D. & Godfray, H. C. J. Stable Coexistence in Insect Communities Due to Density- and Trait-Mediated Indirect Effects. Ecology 86, 3182-3189 (2005).


```{r}
Origvv<-function(Time=c(), State, Pars){  
  with(as.list(c(State, Pars)),{  
    dB <-  B*rB*(1- a*B - a12*C) - (aA*B*A)/(1+b*B+w*C)
    dC <-  C*rC*(1- a*C - a21*B)  
    dA <-  (s*aA*B*A)/(1+b*B +d*A+w*C) - A*m
    return(list(c(dB, dC,dA)))
  })
}

pars<- OrigPars<-list(
  a  =0.000382,
  a12=0.00037,
  a21=0.000397,
  rB =3.22,
  rC =2.82,
  aA =0.281,
  s  =0.5,
  d  =1.26,
  b  =0.0233,
  m  =0.634,
  w=0.0434
)

```

```{r echo=FALSE}
dBdt <-  expression(B*rB*(1- a*B - a12*C) - (aA*B*A)/(1+b*B+w*C) )
dCdt <-  expression(C*rC*(1- a*C - a21*B)     )       
dAdt <-  expression((s*aA*B*A)/(1+b*B +d*A+w*C) - A*m)


{
  # Elements of Jacobian Needed
  cat(paste0('dAdt/dB = '))
  dAdt_dB<-Deriv(dAdt, x = 'B', cache.exp = FALSE)
  print(dAdt_dB)
  
  cat(paste0('dBdt/dA = '))
  dBdt_dA<-Deriv(dBdt, x = 'A', cache.exp = FALSE)
  print(dBdt_dA)
  
  
  cat(paste0('dBdt/dC = '))
  dBdt_dC<-Deriv(dBdt, x = 'C', cache.exp = FALSE)
  print(dBdt_dC)
  
  cat(paste0('dAdt/dC = '))
  dAdt_dC<-Deriv(dAdt, x = 'C', cache.exp = FALSE)
  print(dAdt_dC)
  
  # Derivatives of Jacobian w.r.t. Modifier
  
  cat(paste0('dAdt/dB/dC',' = '))
  dAdt_dB_dC<-Deriv(dAdt_dB, x = 'C', cache.exp = FALSE)
  print(dAdt_dB_dC)
  
  cat(paste0('dBdt/dA/dC ='))
  dBdt_dA_dC<-Deriv(dBdt_dA , x = 'C', cache.exp = FALSE)
  print(dBdt_dA_dC)
}

```

```{r, echo=FALSE}

param.list= c(seq(0, 0.02, l=40), seq(0.02, 0.08,l=60))

param='w'
repeats=200

FUNC=Origvv

FUNC2<-function(Abund, Parms){  
  with(as.list(c(Abund, Parms)),{
    dB <-  B*rB*(1- a*B - a12*C) - (aA*B*A)/(1+b*B+w*C)
    dC <-  C*rC*(1- a*C - a21*B)  
    dA <-  (s*aA*B*A)/(1+b*B +d*A+w*C) - A*m
    return(c(dB, dC,dA))
  })  
}

clist<- data.frame(param=param.list, # set of TIM parameters to run through
                   B=NA,C=NA, A=NA,
                   mu=NA,  
                   dAdt_dB_dCJAC=NA,dBdt_dA_dCJAC=NA,
                   dBdt_dC=NA, dAdt_dC=NA,
                   NewISRatio=NA,
                   FluxAbsChange=NA, FluxRelChange=NA,
                   dAdt_dB_dCInvJAC= NA , dBdt_dA_dCInvJAC = NA)

# For finding New IS difference with TIM, calculate B equilbirum without TIM effect:
pars2=pars
pars2[['w']] <-0  # Remove the TIM effect
outs2<- matrix(NA, ncol=3, nrow=repeats)
for(i in 1:repeats){
  outs2[i,]<-multiroot(FUNC2, c(B=runif(1,10,2000), C=runif(1,1000,2100),A=runif(1,35,100)),parms=pars2, positive = T)$root
}
un<-unique(outs2); colnames(un)<- c('B','C','A');
as.data.frame(un) %>% filter(A>0.0001) ->x # select positive equilbira
if(nrow(x)>0){
  x%>%slice(1) ->x # Just pick out one (NB if multiple equilibira may get problems here!)
  BstarNoTIM =x$B      
  FluxNoMod <-  with( pars2, (aA*x$B*x$A)/(1+b*x$B+w*x$C)   )   
}else{warning("Didn't find equilbirum")}

for(j in 1:nrow(clist)){
  pars[[param]] <- clist$param[j]  
  # Find Aositive Equilbirum: 
  outs<- matrix(NA, ncol=3, nrow=repeats)
  for(i in 1:repeats){
    outs[i,]<-multiroot(FUNC2, c(B=runif(1,10,2000), C=runif(1,1000,2100),A=runif(1,35,100)),parms=pars, positive = T)$root
  }
  un<-unique(outs); colnames(un)<- c('B','C','A');
  as.data.frame(un) %>% filter(A>0.0001 & C>0.0001) ->x # select positive equilbira
  parsALL<- pars 
  if(nrow(x)>0){
    x %>% slice(1) ->x # Just pick out one (NB if multiple equilibira may get problems here!)
    clist$B[j]<-parsALL$B<-x[[1]]
    clist$C[j]<-parsALL$C<-x[[2]]
    clist$A[j]<-parsALL$A<-x[[3]]
    clist$mu[j] <- with(parsALL,  -w * C )
    clist$NewISRatio[j]<- x[[1]] / BstarNoTIM
    clist$dAdt_dB_dCJAC[j]<-with(parsALL,  eval(dAdt_dB_dC)) # dAdt_dB_dC
    clist$dBdt_dA_dCJAC[j]<-with(parsALL,  eval(dBdt_dA_dC)) # dBdt_dA_dC
    clist$dBdt_dC[j]<-with(parsALL,  eval(dBdt_dC))
    clist$dAdt_dC[j]<-with(parsALL,  eval(dAdt_dC))
    clist$FluxAbsChange[j] <- with(parsALL,  (aA*B*A)/(1+b*B+w*C))  - FluxNoMod  ##!
    clist$FluxRelChange[j] <- with(parsALL,  (aA*B*A)/(1+b*B+w*C))/FluxNoMod    ##!!
    
    x %>% as.numeric ->Eq
    
    y<- matrix(rootSolve::gradient(function(x){
      jac<- jacobian.full(c(B=Eq[1], C=x, A=Eq[3]),FUNC, parms=pars, pert=1e-6)
      inv(-jac)}, Eq[2]),nrow=3)
    
    clist$dAdt_dB_dCInvJAC[j]<-y[3,1] 
    clist$dBdt_dA_dCInvJAC[j]<-y[1,3]
  }else{warning("Didn't find equilbirum")}
}

```


# Plotting all together

```{r, echo=FALSE}
NumReps = length(param.list)

require(ggplot2)

# Rescale 
clist %>%
  select(-c(B,C,A))%>%
  gather('Metric','Value', 2:11)  %>%
  group_by(Metric)%>%
  summarise(Scalor = max(abs(Value))) %>% 
  select(Scalor)%>%
  unlist %>%
  as.numeric %>%
  rep(each=NumReps) -> scalers


##need to make sure equations incoroprate this! Especially Mu!!


colnames(clist)

cats<-data.frame(Metric=c("B",                 
                          "C",            
                          "A",            
                          "mu",            
                          "dAdt_dB_dCJAC",   
                          "dBdt_dA_dCJAC",
                          "dBdt_dC",  
                          "dAdt_dC",  
                          "NewISRatio", 
                          "FluxAbsChange", 
                          "FluxRelChange" ,
                          "dAdt_dB_dCInvJAC",
                          "dBdt_dA_dCInvJAC"),metricCategory=
                   c('Population',
                     'Population'    ,
                     'Population'    ,
                     'Flux Change',
                     'Derivatives of Jacobian',
                     'Derivatives of Jacobian',
                     'Jacobian Elements',
                     'Jacobian Elements',
                     'Flux Change' ,
                     'Flux Change',
                     'Flux Change',
                     'Derivatives of Inverse Jacobian',
                     'Derivatives of Inverse Jacobian'),
                 Direction=
                   c('Neither',
                     'Neither'    ,
                     'Neither'    ,
                     'Neither',
                     'B on A',
                     'A on B',
                     'B change',
                     'A Change',
                     'Neither' ,
                     'Neither',
                     'Neither',
                     'B on A',
                     'A on B'))
#  mutate(Scaled = Value /scalers ) %>%

clist %>% 
  gather('Metric','Value', 2:14) %>% 
  left_join( cats, by='Metric' ) %>%
  arrange(Metric) -> VVDATA

# VVDATA %>%
#   mutate(absValues =abs(Value))%>%
#   ggplot(aes(y=absValues, x=param, col=Metric, shape= Direction)) +
#   geom_point() +
#   geom_line() +
#   scale_color_brewer(palette = 'Paired') +
#   facet_grid(metricCategory~., scales = 'free_y')


```


```{r}

bind_rows(LINEARDATA %>% rename(param=c)%>% mutate(Data='Linear'),
          NONLINEARDATA %>% rename(param=c)%>% mutate(Data='Non-Linear'), 
          VVDATA%>% mutate(Data='VV')
) -> all


all$Population<-'A'
all$Population[all$Metric =='B'] <- 'B'
all$Population[all$Metric =='C'] <- 'C'
#all$Population<-as.factor(all$LineType)

# order facets to same as table
all$metricCategory <- factor(all$metricCategory, levels=c( "Population", "Flux Change",
   "Jacobian Elements" ,"Derivatives of Jacobian" ,
   "Derivatives of Inverse Jacobian" ))


facet_names <- c(`Population` = 'Equilibrium\nPopulations',
                 `Flux Change`=  'Direct Metrics',
                 `Jacobian Elements`=  'Jacobian\nElements',
                 `Derivatives of Jacobian`=  'Derivatives\nof Jacobian',
                 `Derivatives of Inverse Jacobian` = 'Derivatives of\nInverse Jacobian',
                  `VV`='Aphid-Parasitoid\n(van Veen et al 2005)'
                 )

b<-c(brewer.pal(10, 'Paired'), 'black')

# Set up colours,
colourset<- c('dBdt_dA_dCInvJAC' = b[1],
             'dBdt_dA_dCJAC'  = b[3],
             'dBdt_dC' = b[5],
             'dAdt_dB_dCInvJAC' =  b[2],
             'dAdt_dB_dCJAC' =b[4],
             'dAdt_dC' = b[6],
             'FluxAbsChange'= b[7],
             'FluxRelChange'= b[8],
             'B' =b[11],
             'mu'= b[9],
             'NewISRatio' = b[10],
             'A' =b[11],
             'C' =b[11])

#all %>% filter( Data=='VV' & metricCategory=='Flux Change')

# Colour changer                                
Nice = 'black'

all %>%
  filter(Data=='Linear')%>%
 ggplot(aes(y=Value, x=param, colour=Metric, linetype = Population)) +
  ylab('                                         Metric Values                                           Densities')+
  xlab('TIM Parameter')+
  geom_line(size=1) +
  scale_colour_manual(values = colourset)+
  facet_grid(metricCategory~Data, scales = 'free')+
  theme(legend.position = "none", strip.text.y = element_blank(),text= element_text(colour=Nice),
        line=element_line(colour=Nice),
        axis.text=element_text(colour=Nice),
        axis.line.x=element_line(colour=Nice),
        strip.background=element_rect(fill ='white' ),
        axis.line.y=element_line(colour=Nice),
        axis.ticks.x=element_line(colour=Nice),
        axis.ticks.y=element_line(colour=Nice))-> A 

all %>%
  filter(Data=='Non-Linear')%>%
 ggplot(aes(y=Value, x=param, colour=Metric, linetype = Population)) +
  ylab('')+ xlab('TIM Parameter')+
    scale_colour_manual(values = colourset)+
  geom_line(size=1) +
  facet_grid(metricCategory~Data, scales = 'free')+
  theme(legend.position = "none",
        strip.text.y = element_blank(),
        text= element_text(colour=Nice),
        strip.background=element_rect(fill ='white' ),
        line=element_line(colour=Nice),
        axis.text=element_text(colour=Nice),
        axis.line.x=element_line(colour=Nice),
        axis.line.y=element_line(colour=Nice),
        axis.ticks.x=element_line(colour=Nice),
        axis.ticks.y=element_line(colour=Nice)) -> B


labels=c(expression(mu),
         'Absolute\nFlux Change',
         'Relative\nFlux Change',
         'New IS Ratio\nChange',
         expression(J[AC]),
         expression(J[BC]), 
         expression(frac(delta~{J}[AB],delta~C)),
         expression(frac(delta~{J}[BA],delta~C)),
         expression(frac(delta~{-J^-1}[AB],delta~C)),
         expression(frac(delta~{-J^-1}[BA],delta~C)))  

all %>%
  filter(Data=='VV' & Metric != 'FluxAbsChange') ->vvDATA2 

# log aphid and wasps populations
vvDATA2$Value[vvDATA2$metricCategory=='Population']<-log(vvDATA2$Value[vvDATA2$metricCategory=='Population'] )

vvDATA2$Metric <- factor(vvDATA2$Metric, levels=c( 'A','B','C',
                                                   'mu','FluxAbsChange','FluxRelChange','NewISRatio',
                                                   'dAdt_dC', 'dBdt_dC',
                                                   'dAdt_dB_dCJAC','dBdt_dA_dCJAC',
                                                   'dAdt_dB_dCInvJAC','dBdt_dA_dCInvJAC'))
vvDATA2%>%
  ggplot(aes(y=Value, x=param, col= Metric, linetype = Population))+
  ylab('')+xlab('TIM Parameter')+
  geom_line(size=1) +
  scale_y_continuous(labels=function(n){format(n, scientific = FALSE)})+
  scale_colour_manual(values = colourset,
                      breaks= c(  'mu','FluxAbsChange','FluxRelChange','NewISRatio',
                                  'dAdt_dC', 'dBdt_dC',
                                  'dAdt_dB_dCJAC','dBdt_dA_dCJAC',
                                  'dAdt_dB_dCInvJAC','dBdt_dA_dCInvJAC') ,
                      labels=labels, drop=FALSE)+
  scale_linetype_discrete(breaks= c('A','B','C'))+
  theme(text= element_text(colour=Nice),
        line=element_line(colour=Nice),
        axis.text=element_text(colour=Nice),
        strip.background=element_rect(fill ='white' ),
        axis.line.x=element_line(colour=Nice),
        axis.line.y=element_line(colour=Nice),
        axis.ticks.x=element_line(colour=Nice),
        axis.ticks.y=element_line(colour=Nice),
        legend.text.align = 0,
        legend.key = element_rect(colour = Nice),
        legend.key.height=unit(2.5,"line")
        
  )+
 guides(colour=guide_legend(order=2),
        linetype=guide_legend(order=1,override.aes = list(colour = 'black')))+
  facet_grid(metricCategory~Data, scales = 'free',labeller = as_labeller(facet_names)) -> C#

```

```{r, fig.height=8, fig.width=12, message=FALSE, warning=FALSE}

plot_grid(A, B, C,  labels = c("", "", ""), align = "h", nrow = 1, rel_widths = c(1.5,1.5,2.5)) 

plot_grid(A, B, C,  labels = c("", "", ""), align = "h", nrow = 1, rel_widths = c(1.5,1.5,2.5)) %>%
    ggsave('MetricComparison.pdf',., width = 12, height=8,bg="white", dpi = 400)

```








